---
title: "DD_RPS"
author: "Julia Parish"
date: "3/3/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(stargazer)
library(estimatr)
library(plm)
library(sandwich)
library(lmtest)
library(tidyverse)
library(here)
```

# IMPORT CSV DATA 

```{r}
RPS <- read.csv(here("data/RPS_data.csv"))
```


# SUMMARY STATISTICS

```{r}
stargazer(RPS, type="text", digits=2)
```
*will be on FINAL*

# LIST SOME VARIABLES FOR CALIFORNIA

```{r}
RPS%>%
  filter(state_name == "California")%>%
  select(state_name, year, rps_D, rps_ever_adopter, rps_implementation_year)%>%
  View
```

# DD REGRESSION, Y = Wind+Solar installed capacity (MW), using lm package

```{r}
#lm package due to not having a number of factors
DD_cap1 <- lm(formula = cap_WS_mw ~ rps_D + as.factor(state_name) + as.factor(year), data=RPS)
# calculating standard errors w/o cluster robust
se_DD_cap1 <- starprep(DD_cap1, stat = c("std.error"), se_type = "HC2", alpha = 0.05) 

DD_cap2 <- lm(formula = cap_WS_mw ~ rps_D + as.factor(state_name) + as.factor(year), data=RPS)
# calculating standard errors w/ cluster robust
se_DD_cap2 <- starprep(DD_cap2, stat = c("std.error"), se_type = "CR2", clusters=RPS$state_name, alpha = 0.05) 

se_models <- list(se_DD_cap1[[1]], se_DD_cap2[[1]])
stargazer(DD_cap1, DD_cap2, se = se_models, keep=c("rps_D"), type="text")
```

### Col 1: beta1 increase renewable energt capacity by 546 mg w/ se: 128, 3 stars, 

# DD REGRESSION, Y = Wind+Solar generation (GWh), using plm package

```{r}
DD_gen1 <- plm(gen_WS_gwh ~ rps_D, 
               index = c("state_name", "year"), model = "within", effect = "twoways", data = RPS)
```

# Calculate standard errors (note slightly different procedure with plm package)

```{r}
se_DD_gen1 <- coeftest(DD_gen1, vcov = vcovHC(DD_gen1, type = "HC2"))[, "Std. Error"]
```

# Reformat standard errors for stargazer()

```{r}
se_DD_gen1 <- list(se_DD_gen1)
```

# Output results with stargazer

```{r}
stargazer(DD_gen1, keep=c("rps_D"), se = se_DD_gen1, type="text")
```

# rps have increased renewable energy sources by 2,387 mw
