---
title: "IVR lab"
author: "Julia Parish"
date: "2/10/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = FALSE}
library(stargazer)
library(estimatr)
library(AER) 
library(ggplot2)
library(cowplot)
library(sandwich)
library(lmtest)
library(dplyr)
library(lfe) # https://cran.r-project.org/web/packages/lfe/lfe.pdf
library(here)
```

```{r}

# IMPORT CSV DATA
FULTON <- read.csv(here("data/FULTON.csv")) %>%
  mutate(log_tots = log(tots), # total sales
         log_price = log(pricelevel)) # log total price

# SUMMARY STATISTICS
stargazer(FULTON, type="text", digits=2)
```

```{r}
# BASIC OLS REGRESSION
# log price is continuous, not binary
ols <- lm(formula = log_tots ~ log_price, data=FULTON)

summary(ols)
```
# log_price interpretation: if the price was to go up by 1% then the quantity sold drops by 0.6%; y goes down by 0.6% then intercept isn't interpretable. Intercept is only interpretable if dummy 


# what is the effect of windspeed on the price of fish? 
```{r}
# FIRST_STAGE REGRESSION - JUST-IDENTIFIED MODEL
fs1 <- lm(formula = log_price ~ windspd, data=FULTON)
summary(fs1)
```

# a 1m increase in windspeed increases the price of fish by 0.7% but does effect the demand of fish
# reject pi1 = 0

```{r}
# TSLS - JUST-IDENTIFIED MODEL

# log quantity on log price, | used to delineate instruments, instrument is windspeed
tsls1 <- ivreg(log_tots ~ log_price | windspd, data = FULTON) 
summary(tsls1)
```

Now -1.4 ; can argue this is not bias by demand forces, the price is influenced by winspeed not demand. 

```{r}
# Calculate robust standard errors for OLS and FS1 using starprep()
se_ols_fs1 <- starprep(ols,fs1, stat = c("std.error"), se_type = "HC2", alpha = 0.05) 

# Calculate robust standard errors sandwich and lmtest packages (starprep() does not like ivreg() objects)
se_tsls11 <- coeftest(tsls1, vcov = vcovHC(tsls1, type = "HC2"))[, "Std. Error"]

# Combine standard errors and output results with stargazer()
se_models <- append(se_ols_fs1,list(se_tsls11))
stargazer(ols, fs1, tsls1, se = se_models, type="text")
```

```{r}
# Other approach using the lfe package #####################
# Estimate the first two models
ols_felm <- felm(formula = log_tots ~ log_price, data=FULTON)
fs1_felm <- felm(formula = log_price ~ windspd, data=FULTON)
# Estimate 2SLS
# "log_tots ~ 1" is not the first stage, it is the all variables in the first stage, BUT the endogenous one
# | 0 | means that we are not including fixed effects here.
tsls1_felm <- felm(formula = log_tots ~ 1 | 0 | (log_price ~ windspd),  data=FULTON)
# The robust standard errors are calculated (not reported) by default in felm(), so here we can fetch and combine them
# It might be HC1, but the documentation is not great. 
se_models_felm <- list(ols_felm$rse,fs1_felm$rse, tsls1_felm$rse)
stargazer(ols_felm, fs1_felm, tsls1_felm, se = se_models_felm, type="text")
```